\textbf{Hardware accelerator topologies in heterogeneous systems: an evaluation in the security domain}

### 2019-12-07 reports/paper.tex
update report

\begin{figure}
  \centering
  \include{media/simonround}
  \caption{Simon's round function Feistel stepping. \textbf{S\textsuperscript{i}} are
    circular left shifts by i bits; \textbf{\&} is a bitwise \texttt{AND}
    operation and $\oplus$ are bitwise \texttt{XOR} operations.}
  \label{fig:simonround}
\end{figure}

@@

The memory-mapped accelerator can operate in two different ways: i) unattended
operation --- ECB mode only, in which all necessary rounds are performed over a word until
completion of encryption/decryption process, or ii) interactive operation, where
software issues one round at a time, which enables software implementation of
CBC or other modes.

@@

\section{Evaluation}

>>>>

\begin{figure}
  \centering
  \include{media/simonround}
  \caption{Simon's round function Feistel stepping. \textbf{S\textsuperscript{j}} are
    circular left shifts by j bits; \textbf{\&} is a bitwise \texttt{AND}
    operation and $\oplus$ are bitwise \texttt{XOR} operations.}
  \label{fig:simonround}
\end{figure}

@@

The memory-mapped accelerator can operate in two different ways: i) automatic
operation --- ECB mode only, in which all necessary rounds are performed over a word until
completion of encryption/decryption process, or ii) interactive operation, where
software issues one round at a time, which enables software implementation of
CBC or other modes.

@@

\section{Evaluation results}

\subsection{Performance}

To evaluate performance, we consider the case where a plaintext block with a size of
1 kB is encrypted using different implementations of the Simon cipher, yielding
eight different benchmarks:

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{media/ecb_speedup}
  \caption{Speedup using different accelerator configurations in ECB mode.}
  \label{fig:ecbspeedup}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{media/cbc_speedup}
  \caption{Speedup using different accelerator configurations in CBC mode.}
  \label{fig:cbcspeedup}
\end{figure}

\subsection{Area}
